Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-10-08 draft_lm1.tex
minor changes

Let the number of susceptibles to a given dengue virus ($DENV_i$), $S_i$ be 
represented by a Binomial random variables $S_i \sim Bin(n, p_i)$ where $n$ is 
population size and p is the true proportion of susceptibles to $DENV_i$ in 
the population, with $i \in  \{1, 2, 3, 4\}$. In the absence of 
cross-immunity, i.e., the exposure to serotypes are independent, the 
total number of susceptibles $S_T=\sum_i S_i$  should follow a Poisson-Binomial 
distribution, $PoisBin(p_i,n)$, where
\begin{equation}
 P(S_T=k) = \sum \prod_i p_i \prod_i  (1-p_i)
\end{equation}

@@

Let $S_{0T}$ and $S_{fT}$, be the total number of susceptibles before and 
after an epidemic, respectively. The total number of cases observed in an 
epidemic, $I_T = \sum_i I_i$ can be expressed as $S_{0T}-S_{fT}$, thus
\begin{align}
 S_{fT} &= S_{0T} - I_T\\
 &=\sum S_i - \sum I_i\\
 &=\sum_i S_i-I_i
\end{align}

If $S_i/n \approx p_i$ and $I_i$ is observed, we can adjust the initial 
$p_i$ proportionately to $I_i$.
\todo[inline]{sera que da para fazer inferencia bayesiana aqui?}

>>>>

Let the number of susceptibles to a given dengue virus ($DENV_i$), $S_i$ be 
represented by a Binomial random variables $S_i \sim Bin(n, p_i)$ where $n$ is 
population size and p is the true proportion of susceptibles to $DENV_i$ in 
the population, with $i \in  \{1, 2, 3, 4\}$. In the absence of 
cross-immunity, i.e., the exposure to serotypes are independent, the 
total number of susceptibles $S_T=\sum_i S_i$  should follow a Poisson-Binomial 
distribution, $PoisBin(p_i,n)$, where
\begin{equation}
 P(S_T=k) = \sum \prod_i p_i \prod_i  (1-p_i)
\end{equation}
\todo[inline]{this sum is over all types of susceptibles, I think: 
$\{S_{1}, S_{2}, 
S_{3},S_{4},S_{12},S_{123},S_{1234},S_{13},S_{14},S_{23},S_{234},S_{24},S_{34}\}
$}

@@

Let $S_{0T}$ and $S_{fT}$, be the total number of susceptibles before and 
after an epidemic, respectively. The total number of cases observed in an 
epidemic, $I_T = \sum_i I_i$ can be expressed as $S_{0T}-S_{fT}$, thus
\begin{align}
 S_{fT} &= S_{0T} - I_T\\
 &=\sum S_{0i} - \sum I_i\\
 &=\sum_i S_{0i}-I_i
\end{align}

If $S_i/n \approx p_i$ and $I_i$ is observed, we can adjust the initial 
$p_i$ according to $I_i$.
\todo[inline]{sera que da para fazer inferencia bayesiana aqui?}
